A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-30 sections/model_overview/main.tex
Highlight choice of queue and potential extensions
Rewrite the whole paragraph so that the choice of unobservable queues
is highlighted and clearly state the potential new extensions

Here, \(\alpha\) represents the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked. 
Note here that the choice of \(p_A\) and \(p_B\) rely solely on equation
\ref{eq:obj_distributor}.
An extension that can be applied here is the use of unobservable queues.
The ambulance service does not necessarily know at which state hospitals A and
B are at, and thus may need to make decisions based on other
information~\cite{unobservablequeue}.
While this is not an unrealistic scenario it is outside of the scope of this
paper.
There are several other factors that can affect the routing of the patients 
that are also outside the scope, for example the distance of each hospital or
even the priority level of each patient.

>>>>

Here, \(\alpha\) represents the ``importance'' of each objective,
where high \(\alpha\) indicates a higher weight on the proportion of lost 
individuals and smaller \(\alpha\) a higher weight on the time blocked. 
The choice of \(p_A\) and \(p_B\) rely solely on equation
\ref{eq:obj_distributor}.
Note that the current system is modelled using unobservable queues which is not
necessarily an unrealistic approach~\cite{unobservablequeue}.
However, there are several other factors that can affect the routing of the
patients that are outside the scope of this paper.
For example the distance from each hospital or even the priority level of each
patient may be a significant factor that affects the ambulance service's
decision.
